---
title: "Is there a relationship between the level of crime in Australia and tourism?"
author: Collaborators
output:
  pdf_document:
    citation_package: natbib
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 2
    keep_tex: true
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
bibliography: references.bib 
biblio-style: plainnat
subtitle: "Machine learning consultancy"
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center} 
  \includegraphics[width=5in,height=6in]{Images/sam-albury-oA7MMRxTVzo-unsplash.jpg}\LARGE\\}
- \posttitle{\end{center}}
- \usepackage{fontawesome}
- \usepackage[most]{tcolorbox}
- \usepackage{xcolor}
- \usepackage{sectsty}
- \sectionfont{\color{blue}}
- \usepackage{verbatim}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
---


```{r , echo = FALSE, message = FALSE, warning = FALSE}

library(knitr)
library(kableExtra)
library(tidyverse)
library(kableExtra)
```

# Intro

\clearpage

# Methodology

\clearpage

# Data

```{r read-data}
# clean the data set
crime <- read_csv(here::here("Data", "SYB62_328_201904_Intentional Homicides and Other Crimes.csv")) %>%
  clean_names() %>%
  rename(Country_id = t12, Country = intentional_homicides_and_other_crimes, Year = x3, Series = x4, Value = x5, footnotes = x6, Source = x7)
crime_clean <- crime[-1,]
tourism <- read_csv(here::here("Data", "SYB63_176_202003_Tourist-Visitors Arrival and Expenditure.csv")) %>%
  clean_names() %>%
  rename(Country_id = t33, Country = tourist_visitor_arrivals_and_tourism_expenditure, Year = x3, Series = x4, Tourism_arr_type = x5, Tourism_arr_footnote = x6, Value = x7, Footnotes = x8, Source = x9)
tourism_clean <- tourism[-1,]
```


\clearpage

# Section 1a

```{r}
#Varsha --> focus on crime trends around the world
crime_world <- crime_clean[,-6] 
names(crime_world)[1] <- "Country_Code"
names(crime_world)[2] <- "region"
names(crime_world)[4] <- "Crimes"
names(crime_world)[6] <- "Source"
crime_world <- crime_world %>%  arrange(region, Year)
```

We are looking at the crime rate throughout the world and the mean values of each of the `r distinct(crime_world$Crimes)` crimes in each of the `r distinct(crime_world$region)`  different regions, this dataset is from the UN website. This section covers the overall crime rate in the world data and what kind of crimes are at large in different parts of the world. 

```{r crimerates}
crime_rate <- crime_world %>% group_by(Year,Crimes,region) %>% 
   count(Crimes)
ggplot(crime_rate,
       aes(x = Year,
           y = n,
           color = Crimes, fill = Crimes)) + 
  theme(axis.text.x = element_text(angle = 90)) +
  geom_col()
```

The plot \@ref(fig:crimerates) depicts a column graph with year on the x-axis and counts on the y-axis, where the 


```{r worldmap}
require(maps)
world_map <- map_data("world")
crimemap <- merge(world_map,crime_world, by = "region") 
  #pivot_wider(names_from = "Crimes", values_from = "Value")
```


```{r worldmapdata}
library(viridis)
crime_world_map <- crimemap %>% filter(Year %in% c(2005,2010,2015,2016))
ggplot(crime_world_map, 
       aes(x = long, 
           y = lat, 
           group = group,
           fill = Crimes)) +
  geom_polygon(colour = "grey90") + theme_classic()+
  #scale_fill_viridis_c(guide = "legend") + 
  scale_x_continuous() +scale_y_continuous() 
```


\clearpage

# Section 1b

```{r}

#Yawen --> focus on crime in Australia
```

\clearpage

# Section 2a

```{r}

#Mayunk --> focus on tourism trends around the world
```

\clearpage

# Section 2b

```{r}

#Ankush --> focus on tourism in Australia
```

\clearpage

# Section 3

```{r}

#Yuheng --> Relationship between Crime and Tourism
```

\clearpage

# References
