---
title: "Is there a relationship between the level of crime in Australia and tourism?"
author: Collaborators
output:
  pdf_document:
    citation_package: natbib
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 2
    keep_tex: true
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
bibliography: references.bib 
biblio-style: plainnat
subtitle: "Machine learning consultancy"
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center} 
  \includegraphics[width=5in,height=6in]{Images/sam-albury-oA7MMRxTVzo-unsplash.jpg}\LARGE\\}
- \posttitle{\end{center}}
- \usepackage{fontawesome}
- \usepackage[most]{tcolorbox}
- \usepackage{xcolor}
- \usepackage{sectsty}
- \sectionfont{\color{blue}}
- \usepackage{verbatim}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
---


```{r , echo = FALSE, message = FALSE, warning = FALSE}

library(knitr)
library(kableExtra)
library(tidyverse)
library(kableExtra)
```

# Intro

\clearpage

# Methodology

\clearpage

# Data

```{r read-data}
# clean the data set
crime <- read_csv(here::here("Data", "SYB62_328_201904_Intentional Homicides and Other Crimes.csv")) %>%
  clean_names() %>%
  rename(Country_id = t12, Country = intentional_homicides_and_other_crimes, Year = x3, Series = x4, Value = x5, footnotes = x6, Source = x7)
crime_clean <- crime[-1,]
tourism <- read_csv(here::here("Data", "SYB63_176_202003_Tourist-Visitors Arrival and Expenditure.csv")) %>%
  clean_names() %>%
  rename(Country_id = t33, Country = tourist_visitor_arrivals_and_tourism_expenditure, Year = x3, Series = x4, Tourism_arr_type = x5, Tourism_arr_footnote = x6, Value = x7, Footnotes = x8, Source = x9)
tourism_clean <- tourism[-1,]
```


\clearpage

# Section 1a

```{r}
#Varsha --> focus on crime trends around the world
crime_world <- crime_clean[,-6] 
names(crime_world)[1] <- "Country_Code"
names(crime_world)[2] <- "region"
names(crime_world)[4] <- "Crimes"
names(crime_world)[6] <- "Source"
crime_world <- crime_world %>%  arrange(region, Year)
```

We are looking at the crime rate throughout the world and the mean values of each of the `r distinct(crime_world$Crimes)` crimes in each of the `r distinct(crime_world$region)`  different regions, this dataset is from the UN website. This section covers the overall crime rate in the world data and what kind of crimes are at large in different parts of the world. The day-to-day incidents of crime such as robbery, burglary, assault and theft — may seem to be largely an urban phenomenon driven by local factors. Urban planning, crime prevention and police action may all appear to play an important role in decreasing the risk of crime victimization is on one end of the spectrum. And at the other end of the spectrum are forms of transnational organized crime, including trafficking in goods and persons, that can involve extended cross-national networks.
Although this data is form a well known data site, the actual crime rate within each country maybe faulty due to fear in constitutional laws within the country or corruption.

```{r crimerates, fig.cap= "Mean crime rates throughout the years"}
crime_rate <- crime_world %>% group_by(Year,Crimes,region) %>% 
   count(Crimes)
ggplot(crime_rate,
       aes(x = Year,
           y = n)) + 
  theme(axis.text.x = element_text(angle = 90)) +
  geom_col()
```
```{r highestcrime, eval=FALSE}
crime_world %>%  
  select(Year,Crimes,Value,region) %>%  
  group_by(region,Crimes) %>%  mutate(maxval = max(Value)) %>% 
  pivot_wider(names_from = "Crimes", values_from = "Value") %>% arrange(desc(`maxval`))
```



The plot \@ref(fig:crimerates) depicts a column graph with year on the x-axis and counts on the y-axis, where the the years in the dataset vary from 2000 through to year 2016, looking at this plot it can be inferred that the rate of crimes in the year 2010 was the highest with a count of more than 750 mean cases throughout the world. Followed by approximate values in 2005, 2015 and 2016 with mean counts of 760, 600 and 500. It also illustrates that with the years the crime rates have been fluctuating rapidly but also with time the crime mean counts have decreased.


```{r worldmap}
require(maps)
world_map <- map_data("world")
crimemap <- merge(world_map,crime_world, by = "region") 
  #pivot_wider(names_from = "Crimes", values_from = "Value")
```

The library maps is a very useful package in the CRAN which helps us R-users visualize the world analysis better (@maps) . Using this maps package for drawing geographical maps ,we can depict the different types of crimes in different countries over the years, the legend on the side depicts the crimes which are most commonly known for. 


```{r worldmapdata}
library(viridis)
crime_world_map <- crimemap %>% filter(Year %in% c(2005,2010,2015,2016))
ggplot(crime_world_map, 
       aes(x = long, 
           y = lat, 
           group = group,
           fill = Crimes)) +
  geom_polygon(colour = "grey90") + theme_classic()+
  #scale_fill_viridis_c(guide = "legend") + 
  scale_x_continuous() +scale_y_continuous() 
```

Research question within this section: 

- The crime rates throughout the world, which type of crime has more mean counts and which country has this identified crime?

--> Going through the entire dataset and the throughout the years, it can be concluded that the crime rates have surely decreased with time , even though there were some years in between which had even less crime rates, but the year 2010 has the highest rates of crimes in the entire world. Looking at the world map figure : \@ref(fig:worldmapdata) we can see that the most crime is by Robbery at the national level,rate per 100,000 population followed by intentional homicide rates per 100.000 in blue and brown respectively. It also depicts the percentage of male and female intentional homicide victims, out of which it can be inferred that the females are mostly the victims of homicides at large throughout the world and the country with most number of Robbery at the national level,rate per 100,000 population  is Canada.

\clearpage

# Section 1b

```{r}

#Yawen --> focus on crime in Australia
```

\clearpage

# Section 2a

```{r}

#Mayunk --> focus on tourism trends around the world
```

\clearpage

# Section 2b

```{r}

#Ankush --> focus on tourism in Australia
```

\clearpage

# Section 3

```{r}

#Yuheng --> Relationship between Crime and Tourism
```

\clearpage

# References
